\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}

\newcommand{ \stopsign } {
\begin{tikzpicture}[baseline=(stop.base)]
    \node[draw=white, double=red, double distance=2pt, fill=red, 
          regular polygon, regular polygon sides=8, inner sep=2pt] (stop) 
          {\textcolor{white}{\textbf{\textsf{!}}}};
\end{tikzpicture}
}

\begin{document}
\pagestyle{empty}

\title{Lab 4 (Centripetal Motion) Rubrics}
% \maketitle

\section*{Core Lab Rubrics (2 Rubrics)}
% 3 + 13 = 16 Rules Across 2 Rubrics

\subsection*{Format Compliance Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [FC-01] Formatting Mechanics } – Writing, spelling, and grammar must be at university levels. Report is organized and has appropriate header structure. Must be typed.
\item \textbf{ [FC-02] No Handwritten Documents } - Including embedded images of handwritten documents.
\item \textbf{ [FC-03] Forbidden Phrase } – Reports are forbidden from using the phrase "\textbf{human error}". 
\end{itemize}

\subsection*{Lab Report Rubric (13 Rules)}
\begin{itemize}
\item \textbf{ [LR-01] Introduction: Provide a Description } –  Describe the main experimental idea in your own words.
\item \textbf{ [LR-02] Introduction:  Explain How Topics Relate } – Tie the lab to the everyday world or a particular scientific application.
\item \textbf{ [LR-03] Procedure: Include Accurate Description } – Explain each of the experimental steps performed.
\item \textbf{ [LR-04] Data: Tables, Graphs, and Plots Included }
\item \textbf{ [LR-05] Data:  Graphs, and Plots Have Axes }
\item \textbf{ [LR-06] Data: Graphs, and Plots Have Correct Units }
\item \textbf{ [LR-07] Data: Tables, Graphs, and Plots Have Titles } – e.g., Title: Distance (m) vs. Time (sec).
\item \textbf{ [LR-08] Questions:  Answer all Questions } 
\item \textbf{ [LR-09] Questions:  Provide Clear Responses } – Provide specific justifications for each answer.
\item \textbf{ [LR-10] Conclusion:  Summarize Results }
\item \textbf{ [LR-11] Conclusion:  Include Specific Sources of Error }
\item \textbf{ [LR-12] Conclusion:  Suggest Improvements }
\item \textbf{ [LR-13] Graph Formal Mathematical Notation Included } –  The report includes some mathematical expression using LaTeX, special characters, or use of an equation editor. 
\end{itemize}

\section*{Lab 4 (Centripetal Motion) Rubrics (10 Rubrics)}
% 4 + 3 + 4 + 3 + 3 + 3 + 3 + 3 + 1 + 3 = 30 Rules Across 10 Rubrics

\subsection*{Experimental Proposal Rubric (4 Rules)}
\begin{itemize}
\item \textbf{ [EP-01] Force Identification } - Correctly identifies the spring tension as the source of $ F_c $.
\item \textbf{ [EP-02] Measurement of $ F_c $ } - Proposes a clear method to measure the static force (using the mass/pan) required to stretch the spring to the target radius.
\item \textbf{ [EP-03] Measurement of $ v $ } - Defines a protocol to calculate velocity, typically using $ v = \frac { 2 \pi r }{ T } $ (where $ T $ is the period of rotation).
\item \textbf{ [EP-04] Radius Definition } - Correctly identifies the center of the circle (the vertical axis) for measuring $ r $.
\end{itemize}

\subsection*{Experimental Proposal Proficiency Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [EQ-01] Proficient } - Clearly defines the objective to verify $ F_c = \frac { m v^2 } { r } $. Identifies all four variables ($ m, v, r, F_c $) and the role of the spring in providing centripetal force.
\item \textbf{ [EQ-02] Developing } - Objective is stated, but missing one or more variable definitions or specific equipment functions.
\item \textbf{ [EQ-03] Incomplete } - Proposal is vague (e.g., "we're going to measure force") or missing entirely.
\end{itemize}

\subsection*{Data Collection Rubric (4 Rules)}
\begin{itemize}
\item \textbf{ [DC-01] Radius Accuracy } - Records the measured distance from the center of the shaft to the bob using the viewing background for alignment.
\item \textbf{ [DC-02] Mass Measurements } - Includes the mass of the rotating bob and the mass added to the pan for static calibration.
\item \textbf{ [DC-03] Trial Consistency } - Includes multiple timing trials (e.g., time for 10 or 20 rotations) to minimize human error and calculate an average period. 
\item \textbf{ [DC-04] Equipment Setup } - Confirms the apparatus was leveled using the leveling screws before data collection.
\end{itemize}

\subsection*{Force Measurement ($F_c$) Proficiency Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [FN-01] Proficient } - Describes using the mass/pan and pulley system to determine the static force required to stretch the spring to a specific radius.
\item \textbf{ [FN-02] Developing } - Mentions measuring force but lacks detail on how the hanging mass relates to the spring tension at the target radius.
\item \textbf{ [FN-03] Incomplete } - No description of how the force ($F_c$) is quantified.
\end{itemize}

\subsection*{Kinematics: Measurement ($ r $) Proficiency Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [KN-01] Proficient } - Correctly identifies the center of the rotating structure (vertical axis) and describes measuring the horizontal distance to the bob's center.
\item \textbf{ [KN-02] Developing } - Measures distance but fails to identify the correct center of rotation or the bob's equilibrium point.
\item \textbf{ [KN-03] Incomplete } - Radius measurement methodology is missing.
\end{itemize}

\subsection*{Kinematics: Calculation ($ v $) Proficiency Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [KD-01] Proficient } - Explains how to calculate $ v $ using the period ($ T $) and radius ($ r $) via $ v = \frac {2 \pi r}{ T } $. Includes a method for timing multiple rotations to reduce error (p. 2).
\item \textbf{ [KD-02] Developing } - Measures time for rotation but does not clearly link it to the linear velocity formula.
\item \textbf{ [KD-03] Incomplete } - Velocity is not calculated or the method is fundamentally flawed.
\end{itemize}

\subsection*{Verification \& Analysis Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [VA-01] Formula Application } - Correctly applies the centripetal force formula: $ F = \frac { m v^2 } { r } $
\item \textbf{ [VA-02] Comparative Analysis } - Compares the calculated centripetal force ($ \frac { mv^2 }{ r } $) against the measured static force ($ m g $ from the mass/pan).
\item \textbf{ [VA-03] Quantitative Error } - Calculates the percent difference/error between the experimental and theoretical force values.
\end{itemize}

\subsection*{Verification \& Analysis Proficiency Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [VB-01] Proficient } - Includes an organized data table. Provides a direct comparison between the measured static force and the calculated centripetal force ($ \frac { mv^2 }{ r } $).
\item \textbf{ [VB-02] Developing } - Data is present but missing units, multiple trials, or the final quantitative comparison.
\item \textbf{ [VB-03] Incomplete } - No calculation of $ \frac { mv^2 }{ r } $ or comparison to measured $ F_c $.
\end{itemize}

\subsection*{Conclusion Rubric (1 Rule)}
\begin{itemize}
\item \textbf{ [CO-01] Address Relationship } - Provides a clear statement on whether the data verifies or falsifies the relationship $ F_c = \frac { m v^2 } { r } $ based on the results.
\end{itemize}

\subsection*{Conclusion Proficiency Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [CP-01] Proficient } - Accurately states if the experimental data verified or falsified the relation $ F_c = \frac { m v^2 } { r } $ based on the results.
\item \textbf{ [CP-02] Developing } - Conclusion is present but lacks a quantitative basis or justification.
\item \textbf{ [CP-03] Incomplete } - No conclusion or summary of findings.
\end{itemize}

\section*{Bonus Rubrics (3 Rubrics)}
% 14 + 9 + 13 = 36 Rules Across 3 Rubrics

\subsection*{Uncertainty Rubric (14 Rules)}
\begin{itemize}
\item \textbf{ [UR-01] Completeness } – Every measurement result must be accompanied by a quantitative statement of its uncertainty to be considered complete.
\item \textbf{ [UR-02] Purpose Validation } – Uncertainty must be used as the primary metric to decide if a result is adequate for its intended purpose.
\item \textbf{ [UR-03] Consistency Verification } – Calculated values must be compared against text values to determine if the difference is consistent with the measurement uncertainty.
\item \textbf{ [UR-04] Percentage Uncertainty } – The ratio between a measurement's uncertainty and its value is calculated using the formula: $( \frac{\delta x}{|x|} ) \times 100\%$
\item \textbf{ [UR-05] Additive Propagation } – When adding two measurements, the final uncertainty must be the sum of their absolute uncertainties: $ (A \pm \delta A) + (B \pm \delta B) = (A + B) \pm (\delta A + \delta B) $
\item \textbf{ [UR-06] Subtractive Propagation } – Similar to addition, when subtracting two measurements, the final uncertainty must be the difference of their absolute uncertainties: $ (A \pm \delta A) - (B \pm \delta B) = (A - B) \pm (\delta A + \delta B) $
\item \textbf{ [UR-07] Multiplicative Propagation } – For multiplication, the uncertainty must be calculated using the fractional sum: $ (A \pm \delta A) \times (B \pm \delta B) = (AB) \left[ 1 \pm \left( \frac{\delta A}{A} + \frac{\delta B}{B} \right) \right] $
\item \textbf{ [UR-08] Divisive Propagation } – Similar to multiplication,  the quotient must be calculated using the fractional sum: $ \frac{(A \pm \delta A)}{(B \pm \delta B)} = \left( \frac{A}{B} \right) \left[ 1 \pm \left( \frac{\delta A}{A} + \frac{\delta B}{B} \right) \right] $
\item \textbf{ [UR-09] Constant Scaling } – When multiplying by a constant, the absolute uncertainty must also be multiplied by that constant: $ k \times (A \pm \delta A) = [kA \pm k\delta A] $
\item \textbf{ [UR-10] Square Root Calculation } – The uncertainty of a square root must be determined using the formula: $ \sqrt{(A \pm \delta A)} = \left( \sqrt{A} \pm \frac{\delta A}{2\sqrt{A}} \right) $
\item \textbf{ [UR-11] Trigonometric Uncertainty } – For functions like, uncertainty must be found by calculating the difference between the mean result and the result using the value plus its uncertainty: $ \theta \pm \delta \theta = tan^{-1}\ \{ \frac {A \pm \delta A}{B \pm \delta B}\ \} = tan^{-1} \{  \left( \frac{A}{B} \right) \left[ 1 \pm \left( \frac{\delta A}{A} + \frac{\delta B}{B} \right) \right]  \} $
\item \textbf{ [UR-12] Small Angle Approximation } – If an angle $\theta$ is near zero, the uncertainty in the ratio can be treated as the uncertainty of the angle measurement in radians: $ \theta \pm \delta \theta \approx sin( \theta \pm \delta \theta) = \frac { A \pm \delta A } { B \pm \delta B } $
\item \textbf{ [UR-13] Statistical Standard Deviation } – Report contains the standard deviation of individual measurements: $ \sigma_x = \sqrt{\frac{1}{N-1} \sum_{i=1}^{N} (x_i - \bar{x})^2} $ 
\item \textbf{ [UR-14] Statistical Mean Uncertainty } – For repeated measurements, reports contain the uncertainty of the mean, calculated as the standard deviation of the mean: $ \sigma_{ \bar{x} } = \frac{\sigma_x}{\sqrt{N}} $
\end{itemize}

\subsection*{Scientific Reporting Rubric (9 Rules)}
\begin{itemize}
\item \textbf{ [SR-01] Methodological Precision } – Limitations in tools and methods must be accounted for when reporting scientific information.
\item \textbf{ [SR-02] Error Acknowledgment } – The report states that no measurement is perfect and that experimental error is inherent to the process.
\item \textbf{ [SR-03] Include Uncertainty ( ± $ \delta x $) } – Measurements from the lab must be reported with a plus or minus attached to them to account for the range of possible values in the specific mathematical format: \textit{Measurement} ± $ \delta x $.
\item \textbf{ [SR-04] Apply Significant Figures } - Care must be taken to report measurements with the proper number of significant figures to avoid reporting "information that we don't know".
\item \textbf{ [SR-05] Least Precise Input Rule } – In calculations, the final answer must be limited to the number of significant figures of the least precise measurement used (e.g., if one value has only 2 significant figures and all the other measurements have more than 2, the result must have 2).
\item \textbf{ [SR-06] Calculator Precision } - The resulting values must be rounded to the correct number of significant figures rather than reporting the full calculator output (e.g., 0.8313995 becomes 0.814). 
\item \textbf{ [SR-07] Deterministic Rounding } – When rounding to the correct number of significant figures, the final digit must be adjusted according to the standard rounding rules to reflect the most accurate and correct significant figures.
\item \textbf{ [SR-08] Unit Inclusion } – All reported measurements and results must include their corresponding scientific units (e.g. s, m, miles).
\item \textbf{ [SR-09] Honest Reporting } – To be considered "scientifically honest", results must not be reported as exact integers if there is any possibility of a range; for example, a "guess" of 19 must include its likely variance (e.g., 19 ± 1 secs).
\end{itemize}

\subsection*{Data and Graphs Rubric (13 Rules)}
\begin{itemize}
\item \textbf{ [DG-01] Prioritize Visual Plots } – Data must be presented as a plot or a graph rather than just a table to ensure rapid and clear communication of the science.
\item \textbf{ [DG-02] Proper Axis Assignment } – The horizontal axis must represent the independent variable (e.g., time), while the vertical axis represents the dependent variable (e.g., height).
\item \textbf{ [DG-03] Axis Labeling } – Plots and graphs must include clearly labeled axes that define the variables being measured (e.g., Time in days vs. Height in mm).
\item \textbf{ [DG-04] Explicit Unit Labeling } – All axes must be labeled with their corresponding units of measurement (e.g., $days, mm, W, A$).
\item \textbf{ [DG-05] Preliminary Relation Identification } – A visual assessment must be made to determine if the data shows a linear relation ($y=mx$) or a non-linear one.
\item \textbf{ [DG-06] Slope Interpretation } – The slope of a linear fit must be interpreted in the context of the physical measurements, such as growth rate in mm/day
\item \textbf{ [DG-07] Trend-line Accuracy } – Using software, a "fit" line must be generated that attempts to go as close to every individual data point as possible.
\item \textbf{ [DG-08] Display the Fit Equation } – The specific mathematical equation reported by the fitting software (e.g., $y=7.1974x$) must be displayed on the plot.
\item \textbf{ [DG-09] Contextual Slope Interpretation } – The slope must be extracted from the equation and interpreted within the context of the physical measurement (e.g., a growth rate of ~7 mm/day) .
\item \textbf{ [DG-10] Visual Fit Validation } – A visual inspection must be conducted to confirm if the chosen fit (e.g., linear) is a "good choice" for the raw data provided.
\item \textbf{ [DG-11] Quadratic Modeling } – For non-linear, concave-down data, a quadratic fit ( e.g.,$y=mx^2$) must be applied to identify higher-order coefficients.
\item \textbf{ [DG-12] Linearization Strategy } – For complex or "exotic" functions, a variable substitution (e.g., $z=x^2$ or $z=cos(x)$) must be used to create a linear relationship to solve for m.
\item \textbf{ [DG-13] Extrapolate Coefficients } – Use the slope of a linearized plot to extrapolate specific physical coefficients, such as the 2nd order coefficient in power calculations.
\end{itemize}

\section*{\stopsign Rules for the AI:}
\begin{itemize}
\item \textbf{ Verify Exact Rule Registry Manifest } - (Totaling (3 + 13) + (4 + 3 + 4 + 3 + 3 + 3 + 3 + 3 + 1 + 3) + (14 + 9 + 13) = 82 Rules Across 15 Rubrics)
\item \textbf{ Never Group Categories } –  If the Rubric lists ``Proper Axis Assignment'' and ``Axis Labeling'' separately, they must remain separate in the audit.
\item \textbf{ Match Exact Names }  – Use the  Rule Name exactly as it appears in the PDF.
\item \textbf{ Point-Mirroring } – Assign exactly 1 point for each Rule and every Rubric, with the exception of the Format Compliance Rubric, which is assigned as either Pass or Fail.
\item \textbf{ Enforce Input Anonymity } – If the report contains any PII, alert the user and refuse to assess the input. 
\end{itemize}

\end{document}

