\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}

\newcommand{ \stopsign } {
\begin{tikzpicture}[baseline=(stop.base)]
    \node[draw=white, double=red, double distance=2pt, fill=red, 
          regular polygon, regular polygon sides=8, inner sep=2pt] (stop) 
          {\textcolor{white}{\textbf{\textsf{!}}}};
\end{tikzpicture}
}

\begin{document}
\pagestyle{empty}

\title{Lab 3 (Little g) Rubrics}
% \maketitle

\section*{Core Lab Rubrics (2 Rubrics)}
% 3 + 13 = 16 Rules Across 2 Rubrics

\subsection*{Format Compliance Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [FC-01] Formatting Mechanics } – Writing, spelling, and grammar must be at university levels. Report is organized and has appropriate header structure. Must be typed.
\item \textbf{ [FC-02] No Handwritten Documents } - Including embedded images of handwritten documents.
\item \textbf{ [FC-03] Forbidden Phrase } – Reports are forbidden from using the phrase "\textbf{human error}". 
\end{itemize}

\subsection*{Lab Report Rubric (13 Rules)}
\begin{itemize}
\item \textbf{ [LR-01] Introduction: Provide a Description } –  Describe the main experimental idea in your own words.
\item \textbf{ [LR-02] Introduction:  Explain How Topics Relate } – Tie the lab to the everyday world or a particular scientific application.
\item \textbf{ [LR-03] Procedure: Include Accurate Description } – Explain each of the experimental steps performed.
\item \textbf{ [LR-04] Data: Tables, Graphs, and Plots Included }
\item \textbf{ [LR-05] Data:  Graphs, and Plots Have Axes }
\item \textbf{ [LR-06] Data: Graphs, and Plots Have Correct Units }
\item \textbf{ [LR-07] Data: Tables, Graphs, and Plots Have Titles } – e.g., Title: Distance (m) vs. Time (sec).
\item \textbf{ [LR-08] Questions:  Answer all Questions } 
\item \textbf{ [LR-09] Questions:  Provide Clear Responses } – Provide specific justifications for each answer.
\item \textbf{ [LR-10] Conclusion:  Summarize Results }
\item \textbf{ [LR-11] Conclusion:  Include Specific Sources of Error }
\item \textbf{ [LR-12] Conclusion:  Suggest Improvements }
\item \textbf{ [LR-13] Graph Formal Mathematical Notation Included } –  The report includes some mathematical expression using LaTeX, special characters, or use of an equation editor. 
\end{itemize}

\section*{Lab 3 (Little g) Rubrics (8 Rubrics)}
% 5 + 6 + 3 + 6 + 7 + 6 + 7 + 4 = 44 Rules Across 8 Rubrics

\subsection*{Data and Measurements Rubric (5 Rules)}
\begin{itemize}
\item \textbf{ [DM-01] Rough Measurement } - Three independent trials of a 1-meter drop recorded; average calculated correctly.
\item \textbf{ [DM-02] Slo-mo Free Fall } - Recorded distance (cm converted to m) and time (from 60 fps video) used to calculate $g$ via $ \Delta y = -\frac{1}{2} g t^2 $.
\item \textbf{ [DM-03] Inclined Plane Leveling } - Documentation of the leveling process ($ a = 0 $) and recording of the specific angle $ \theta $ where the cart begins to move).
\item \textbf{ [DM-04] Rolling Cart: Angles } - Table of three distinct angles calculated using $ \theta = \sin^{-1} \left( \frac{h}{L} \right) $ and corresponding acceleration values.
\item \textbf{ [DM-05] Rolling Cart: Masses } - Comparative data for the cart alone versus the cart with the added 500g hex-head mass.
\end{itemize}

\subsection*{Questions and Analysis Rubric (6 Rules)}
\begin{itemize}
\item \textbf{ [QA-01] - Limitations } - Identifies human reaction time and the small $ \Delta t $ of a 1m fall as primary sources of error (p. 2).
\item \textbf{ [QA-02] - Uncertainty } - Performs uncertainty analysis on the angle measurement; explains that static friction keeps the car still at near-zero angles (p. 3).
\item \textbf{ [QA-03] - Friction Coefficient } - Estimates $ \mu $ (static or rolling) based on the angle where the cart first overcame inertia (p. 3).
\item \textbf{ [QA-04] - Kinematic Analysis } - Uses Excel or similar tool (e.g.: Matlab) to derive $ v(t) $ from position data; calculates $ g $ using the slope ($ a $) and the relationship $ a = g \sin \theta $.
\item \textbf{ [QA-05] - Mass Claim } - Provides a clear claim on whether mass affects $ a $; cites kinematic theory ($ a = gsin(\theta) $) to support findings.
\item \textbf{ [QA-06] - Discrepancies } - Analyzes class-wide data; attributes variations to frame-selection errors or parallax in reading the scale).
\end{itemize}

\subsection*{Deductions and Requirements Rubric (3 Rules)}
\begin{itemize}
\item \textbf{ [DR-01] Units } - Missing or incorrect units for acceleration ($ m/s^2 $), height ( $ m $
), or time ($ s $).
\item \textbf{ [DR-02] Significant Figures } - Failure to maintain appropriate precision (e.g., claiming 6 decimal places for a stopwatch measurement).
\item \textbf{ [DR-03] Graphing } - Missing titles, axis labels, or linear fit equations on the Velocity vs. Time plots.
\end{itemize}

\subsection*{Experiment 1: Rough Measurement Rubric (6 Rules)}
\begin{itemize}
\item \textbf{ [RM-01] Three Trials } - Records three individual trials for acceleration due to gravity ($g$) with units ($m/s^2$).
\item \textbf{ [RM-02] Average } - Correctly calculates the average of the three manual trials.
\item \textbf{ [RM-03] } - Did the student record three distinct trials for the 1-meter wooden block drop?
\item \textbf{ [RM-04] Correct Calculation } - Is the average of the three measurements calculated correctly using $\Delta y = -\frac{1}{2}gt^2$?
\item \textbf{ [RM-05] Report Question 1a } - Provides a critical analysis of limitations, specifically highlighting human reaction time and the difficulty of timing short distances ($1$ m).
\item \textbf{ [RM-06] Report Question 1b } - Does the student identify specific limitations such as human reaction time, air resistance, or the short duration of the fall?
\end{itemize}

\subsection*{Experiment 2: Slo-Mo Free Fall Rubric (7 Rules)}
\begin{itemize}
\item \textbf{ [SF-01] } - Documents the chosen distance and time intervals derived from the 60 fps video.
\item \textbf{ [SF-02] } - Calculates $g$ using the kinematic equation $\Delta y = \frac{1}{2}gt^2$.
\item \textbf{ [SF-03] } - Did the student choose a specific time interval and distance from the 60 fps video?
\item \textbf{ [SF-04] } - Is the calculated value for $g$ based on the video analysis provided with units ($m/s^2$)?
\item \textbf{ [SF-05] } - Is there a qualitative discussion on why different groups might reach different results despite using the same video data?    
\item \textbf{ [SF-06] Report Question 6a} - Analyzes discrepancies between group results, citing variables like frame selection and measurement precision.
\item \textbf{ [SF-07] Report Question 6b} - Does the student calculate the class average for $g$ from the provided table?
\end{itemize}

\subsection*{Experiment 3: Ramp Leveling Rubric (6 Rules)}
\begin{itemize}
\item \textbf{ [RL-01] } - Records the precise angle $\theta$ where the cart overcomes static friction to begin moving.
\item \textbf{ [RL-02] } - Did the student use the correct trigonometric relationship $\theta = \sin^{-1}(\frac{h}{L})$ where $L = 1.22$ m?
\item \textbf{ [RL-03] Report Question 2a } - Performs uncertainty analysis on the track angle $\theta$ and explains why the cart remains stationary at near-zero angles.    
\item \textbf{ [RL-04] Report Question 2b } - Does the explanation account for why the car stands still at small angles (e.g., static friction or measurement uncertainty)?
\item \textbf{ [RL-05] Report Question 3a } - Is there a calculated estimate for the static or rolling friction coefficient based on the angle where movement begins?
\item \textbf{ [RL-06] Report Question 3b } - Correctly estimates the static or rolling friction coefficient based on the angle of initial motion.
\end{itemize}

\subsection*{Experiment 4: Cart Angles Rubric (7 Rules)}
\begin{itemize}
\item \textbf{ [CA-01] } - Successfully acquires and imports position-time data into Excel for three distinct ramp angles.
\item \textbf{ [CA-02] } - Generates a velocity-time graph; extracts acceleration ($a$) from the slope of the linear fit ($v(t) = v_0 + at$).
\item \textbf{ [CA-03] } - Were three distinct angles recorded?
\item \textbf{ [CA-04] } - Is the acceleration ($a$) determined from the slope of the $v(t)$ graph?
\item \textbf{ [CA-05] } - Is the value of $g$ correctly isolated using the relationship $a = g \sin\theta$?    
\item \textbf{ [CA-06] Report Question 4a } - Did the student import data to Excel to create velocity vs. time graphs?
\item \textbf{ [CA-07] Report Question 4b } - Solves for $g$ using the relationship $a = g \sin \theta$ for each trial and discusses the consistency of the results.
\end{itemize}

\subsection*{Experiment 5: Cart Masses Rubric (4 Rules)}
\begin{itemize}
\item \textbf{ [CM-01] Acceleration Measurements } - Measures the acceleration of the cart both with and without the additional 500g mass.
\item \textbf{ [CM-02] Claim Supported by Theory } - Is there a claim made regarding whether mass affects acceleration, supported by kinematic theory ($a = g \sin\theta$ being mass-independent)?    
\item \textbf{ [CM-03] Report Question 5a } - Does the student compare the acceleration of the cart with and without the extra mass?
\item \textbf{ [CM-04] Report Question 5b } - Makes a definitive claim on whether mass affects acceleration, justifying the answer using kinematic theory (where $a$ is independent of mass).
\end{itemize}

\section*{Bonus Rubrics (3 Rubrics)}
% 14 + 9 + 13 = 36 Rules Across 3 Rubrics

\subsection*{Uncertainty Rubric (14 Rules)}
\begin{itemize}
\item \textbf{ [UR-01] Completeness } – Every measurement result must be accompanied by a quantitative statement of its uncertainty to be considered complete.
\item \textbf{ [UR-02] Purpose Validation } – Uncertainty must be used as the primary metric to decide if a result is adequate for its intended purpose.
\item \textbf{ [UR-03] Consistency Verification } – Calculated values must be compared against text values to determine if the difference is consistent with the measurement uncertainty.
\item \textbf{ [UR-04] Percentage Uncertainty } – The ratio between a measurement's uncertainty and its value is calculated using the formula: $( \frac{\delta x}{|x|} ) \times 100\%$
\item \textbf{ [UR-05] Additive Propagation } – When adding two measurements, the final uncertainty must be the sum of their absolute uncertainties: $ (A \pm \delta A) + (B \pm \delta B) = (A + B) \pm (\delta A + \delta B) $
\item \textbf{ [UR-06] Subtractive Propagation } – Similar to addition, when subtracting two measurements, the final uncertainty must be the difference of their absolute uncertainties: $ (A \pm \delta A) - (B \pm \delta B) = (A - B) \pm (\delta A + \delta B) $
\item \textbf{ [UR-07] Multiplicative Propagation } – For multiplication, the uncertainty must be calculated using the fractional sum: $ (A \pm \delta A) \times (B \pm \delta B) = (AB) \left[ 1 \pm \left( \frac{\delta A}{A} + \frac{\delta B}{B} \right) \right] $
\item \textbf{ [UR-08] Divisive Propagation } – Similar to multiplication,  the quotient must be calculated using the fractional sum: $ \frac{(A \pm \delta A)}{(B \pm \delta B)} = \left( \frac{A}{B} \right) \left[ 1 \pm \left( \frac{\delta A}{A} + \frac{\delta B}{B} \right) \right] $
\item \textbf{ [UR-09] Constant Scaling } – When multiplying by a constant, the absolute uncertainty must also be multiplied by that constant: $ k \times (A \pm \delta A) = [kA \pm k\delta A] $
\item \textbf{ [UR-10] Square Root Calculation } – The uncertainty of a square root must be determined using the formula: $ \sqrt{(A \pm \delta A)} = \left( \sqrt{A} \pm \frac{\delta A}{2\sqrt{A}} \right) $
\item \textbf{ [UR-11] Trigonometric Uncertainty } – For functions like, uncertainty must be found by calculating the difference between the mean result and the result using the value plus its uncertainty: $ \theta \pm \delta \theta = tan^{-1}\ \{ \frac {A \pm \delta A}{B \pm \delta B}\ \} = tan^{-1} \{  \left( \frac{A}{B} \right) \left[ 1 \pm \left( \frac{\delta A}{A} + \frac{\delta B}{B} \right) \right]  \} $
\item \textbf{ [UR-12] Small Angle Approximation } – If an angle $\theta$ is near zero, the uncertainty in the ratio can be treated as the uncertainty of the angle measurement in radians: $ \theta \pm \delta \theta \approx sin( \theta \pm \delta \theta) = \frac { A \pm \delta A } { B \pm \delta B } $
\item \textbf{ [UR-13] Statistical Standard Deviation } – Report contains the standard deviation of individual measurements: $ \sigma_x = \sqrt{\frac{1}{N-1} \sum_{i=1}^{N} (x_i - \bar{x})^2} $ 
\item \textbf{ [UR-14] Statistical Mean Uncertainty } – For repeated measurements, reports contain the uncertainty of the mean, calculated as the standard deviation of the mean: $ \sigma_{ \bar{x} } = \frac{\sigma_x}{\sqrt{N}} $
\end{itemize}

\subsection*{Scientific Reporting Rubric (9 Rules)}
\begin{itemize}
\item \textbf{ [SR-01] Methodological Precision } – Limitations in tools and methods must be accounted for when reporting scientific information.
\item \textbf{ [SR-02] Error Acknowledgment } – The report states that no measurement is perfect and that experimental error is inherent to the process.
\item \textbf{ [SR-03] Include Uncertainty ( ± $ \delta x $) } – Measurements from the lab must be reported with a plus or minus attached to them to account for the range of possible values in the specific mathematical format: \textit{Measurement} ± $ \delta x $.
\item \textbf{ [SR-04] Apply Significant Figures } - Care must be taken to report measurements with the proper number of significant figures to avoid reporting "information that we don't know".
\item \textbf{ [SR-05] Least Precise Input Rule } – In calculations, the final answer must be limited to the number of significant figures of the least precise measurement used (e.g., if one value has only 2 significant figures and all the other measurements have more than 2, the result must have 2).
\item \textbf{ [SR-06] Calculator Precision } - The resulting values must be rounded to the correct number of significant figures rather than reporting the full calculator output (e.g., 0.8313995 becomes 0.814). 
\item \textbf{ [SR-07] Deterministic Rounding } – When rounding to the correct number of significant figures, the final digit must be adjusted according to the standard rounding rules to reflect the most accurate and correct significant figures.
\item \textbf{ [SR-08] Unit Inclusion } – All reported measurements and results must include their corresponding scientific units (e.g. s, m, miles).
\item \textbf{ [SR-09] Honest Reporting } – To be considered "scientifically honest", results must not be reported as exact integers if there is any possibility of a range; for example, a "guess" of 19 must include its likely variance (e.g., 19 ± 1 secs).
\end{itemize}

\subsection*{Data and Graphs Rubric (13 Rules)}
\begin{itemize}
\item \textbf{ [DG-01] Prioritize Visual Plots } – Data must be presented as a plot or a graph rather than just a table to ensure rapid and clear communication of the science.
\item \textbf{ [DG-02] Proper Axis Assignment } – The horizontal axis must represent the independent variable (e.g., time), while the vertical axis represents the dependent variable (e.g., height).
\item \textbf{ [DG-03] Axis Labeling } – Plots and graphs must include clearly labeled axes that define the variables being measured (e.g., Time in days vs. Height in mm).
\item \textbf{ [DG-04] Explicit Unit Labeling } – All axes must be labeled with their corresponding units of measurement (e.g., $days, mm, W, A$).
\item \textbf{ [DG-05] Preliminary Relation Identification } – A visual assessment must be made to determine if the data shows a linear relation ($y=mx$) or a non-linear one.
\item \textbf{ [DG-06] Slope Interpretation } – The slope of a linear fit must be interpreted in the context of the physical measurements, such as growth rate in mm/day
\item \textbf{ [DG-07] Trend-line Accuracy } – Using software, a "fit" line must be generated that attempts to go as close to every individual data point as possible.
\item \textbf{ [DG-08] Display the Fit Equation } – The specific mathematical equation reported by the fitting software (e.g., $y=7.1974x$) must be displayed on the plot.
\item \textbf{ [DG-09] Contextual Slope Interpretation } – The slope must be extracted from the equation and interpreted within the context of the physical measurement (e.g., a growth rate of ~7 mm/day) .
\item \textbf{ [DG-10] Visual Fit Validation } – A visual inspection must be conducted to confirm if the chosen fit (e.g., linear) is a "good choice" for the raw data provided.
\item \textbf{ [DG-11] Quadratic Modeling } – For non-linear, concave-down data, a quadratic fit ( e.g.,$y=mx^2$) must be applied to identify higher-order coefficients.
\item \textbf{ [DG-12] Linearization Strategy } – For complex or "exotic" functions, a variable substitution (e.g., $z=x^2$ or $z=cos(x)$) must be used to create a linear relationship to solve for m.
\item \textbf{ [DG-13] Extrapolate Coefficients } – Use the slope of a linearized plot to extrapolate specific physical coefficients, such as the 2nd order coefficient in power calculations.
\end{itemize}

\section*{\stopsign Rules for the AI:}
\begin{itemize}
\item \textbf{ Verify Exact Rule Registry Manifest } - (Totaling (3 + 13) + (5 + 6 + 3 + 6 + 7 + 6 + 7 + 4) + (14 + 9 + 13) = 96 Rules Across 13 Rubrics)
\item \textbf{ Never Group Categories } –  If the Rubric lists ``Proper Axis Assignment'' and ``Axis Labeling'' separately, they must remain separate in the audit.
\item \textbf{ Match Exact Names }  – Use the  Rule Name exactly as it appears in the PDF.
\item \textbf{ Point-Mirroring } – Assign exactly 1 point for each Rule and every Rubric, with the exception of the Format Compliance Rubric, which is assigned as either Pass or Fail.
\item \textbf{ Enforce Input Anonymity } – If the report contains any PII, alert the user and refuse to assess the input. 
\end{itemize}

\end{document}

